---
title: "Homework 6"
author: Yuanxin Zhang
output: github_document
---

This is my solution to Homework 6.
```{r setup, include = FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

## Problem 1

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.

```{r message = FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city. For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities. Extract the adjusted odds ratio (and CI) for solving homicides comparing Black victims to white victims. 

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


## Problem 2

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r message = FALSE}
birthweight_df = 
  read_csv("./data/birthweight.csv") %>% 
  
  mutate(
    babysex = case_when(
      babysex == 1 ~ "Male",
      babysex == 2 ~ "Female"
    ) %>% as.factor(),
    
    frace = case_when(
      frace == 1 ~ "White",
      frace == 2 ~ "Black",
      frace == 3 ~ "Asian",
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other",
      frace == 9 ~ "Unknown"
    ) %>% as.factor(),
    
    malform = case_when(
      malform == 0 ~ "Absent",
      malform == 1 ~ "Present"
    ) %>% as.factor(),
    
    mrace = case_when(
      mrace == 1 ~ "White",
      mrace == 2 ~ "Black",
      mrace == 3 ~ "Asian",
      mrace == 4 ~ "Puerto Rican",
      mrace == 8 ~ "Other",
      mrace == 9 ~ "Unknown"
    ) %>% as.factor()
  )
```

Baby’s sex, father’s race, presence of malformations that could affect weight, and mother’s race were converted to factor. The birthweight dataset has `r birthweight_df %>% nrow()` rows and `r birthweight_df %>% ncol()`columns. There is `r birthweight_df %>% filter(is.na(bwt)) %>% nrow()` missing data in baby’s birth weight (grams).

<br>

I proposed my regression model for birthweight based on the finding of this [paper](https://www.sciencedirect.com/science/article/abs/pii/0002937882906275), which suggests that the sex of the baby, parity, maternal smoking during the pregnancy, maternal height, weight and gestation were significant factors.

```{r}
model1_fit = lm(bwt ~ babysex + parity + smoken + mheight + delwt + gaweeks, data = birthweight_df)

model1_fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

birthweight_df %>% 
  modelr::add_predictions(model1_fit) %>% 
  modelr::add_residuals(model1_fit) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.3) +
  labs(
    title = "Model 1 Residuals Against Fitted Values",
    x = "Fitted value",
    y = "Residual"
  )
```

From the "Model 1 Residuals Against Fitted Values" plot, most residuals randomly scatter around 0, indicating that the assumption of normality for residuals is not violated.

<br>

Compare my model to two others in terms of the cross-validated prediction error:
* Model 2 using length at birth and gestational age as predictors (main effects only)
* Model 3 using head circumference, length, sex, and all interactions (including the three-way interaction) between these.

```{r warning = FALSE}
cv_df =
  crossv_mc(birthweight_df,100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    model_1 = map(train, ~lm(bwt ~ babysex + parity + smoken + mheight + delwt + gaweeks, data = .x)),
    model_2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_3 = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))) %>% 
  mutate(
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
    rmse_model_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

In terms of the cross-validated prediction error, Model 3, which used head circumference, length, sex, and all interactions, is the best model. (the smaller the RMSE, the better the model)


## Problem 3

Import the 2017 Central Park weather data.

```{r message = FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of R-squared and log product of beta coefficients.

```{r}
boot_results =
  weather_df %>% 
  bootstrap(5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)), 
    r_squared = map(models, broom::glance),
    coefficient = map(models, broom::tidy)
  ) %>% 
  select(strap_number, r_squared, coefficient) %>% 
  unnest(r_squared) %>% 
  select(strap_number, r.squared, coefficient) %>% 
  unnest(coefficient) %>% 
  janitor::clean_names() %>% 
  select(strap_number:estimate) %>% 
  pivot_wider(
    everything(),
    names_from = term, 
    values_from = estimate) %>% 
  rename(
    beta_0 = "(Intercept)",
    beta_1 = "tmin"
  ) %>% 
  mutate(log_product_coef = log(beta_0 * beta_1))
```

Plot the distribution of estimates.
```{r}
boot_results %>% 
  ggplot(aes(x = r_squared)) +
  geom_density() +
  labs(
    title = "Distribution of estimate of R-squared",
    x = "R-squared",
    y = "Density"
  ) 

boot_results %>% 
  ggplot(aes(x = log_product_coef)) +
  geom_density() +
  labs(
    title = "Distribution of estimate of log product of beta coefficients",
    x = "Log product of beta coefficients",
    y = "Density"
  ) 
```

The distribution of estimate of R-squared is approximately normal (slightly left-skewed), with the peak around 0.91. The distribution of estimate of log product of beta coefficients is approximately normal, with the peak around 2.02.

Construct bootstrap CI.

```{r}
boot_results %>% 
  summarize(
    r_squared_ci_lower = quantile(r_squared, 0.025),
    r_squared_ci_upper = quantile(r_squared, 0.975)
  ) %>% 
  knitr::kable()
boot_results %>% 
  summarize(
    log_product_coef_ci_lower = quantile(log_product_coef, 0.025),
    log_product_coef_ci_upper = quantile(log_product_coef, 0.975)
  )  %>% 
  knitr::kable()
```
